% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
\documentclass[11pt, a4paper]{../../awesome-cv/awesome-cv}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% --- PERSONAL DATA ---
\name{José Luis}{García Orobio}
\position{Growth Engineer{\enskip\cdotp\enskip}E-commerce Architect}
\address{Mexico (Remote/Hybrid){\enskip\textbar\enskip}Immediate availability}

\email{tu-email@dominio.com}
\homepage{www.xperta.social}
\github{lbaddass}
\linkedin{jlgarciaorobio}
\twitter{lbaddassl}

\quote{``I don't build websites; I build secure, fast sales machines.''}

\begin{document}

% Header
\makecvheader[C]

% --- PROFILE SUMMARY ---
\begin{cvsection}{Profile Summary}
\begin{cvparagraph}
Growth Engineer with a security-first foundation. I design high-performance storefronts that load in milliseconds, resist common vulnerabilities, and convert better. I combine \textbf{CRO}, \textbf{headless architectures}, and \textbf{Shopify/Next.js} to decouple frontend and backend for maximum speed, SEO, and revenue.
\end{cvparagraph}
\end{cvsection}

% --- PERFORMANCE & SECURITY AUDIT ---
\begin{cvsection}{Performance \& Security Audit}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} p{0.32\textwidth} p{0.62\textwidth}}
\textbf{You Get (Employer)} & \textbf{I Provide (The Stack)} \\
\hline
\textbf{Business Logic} & Conversion-first code: every component justifies ROAS/ROI. \\
\textbf{Hybrid Agility} & I connect Marketing needs with architecture decisions without friction. \\
\end{tabular*}
\end{cvsection}

% --- HYBRID IDENTITY STACK ---
\begin{cvsection}{Hybrid Identity Stack}
\begin{cvskills}
  \cvskill
    {Growth Engineer}
    {CRO-driven builds. \textbf{Stack:} Next.js (App Router), Tailwind CSS, Vercel.}

  \cvskill
    {E-commerce Architect}
    {Shopify at scale and funnel re-engineering. \textbf{Stack:} Shopify Liquid, Klaviyo, Recharge.}

  \cvskill
    {Security-First Dev}
    {Resilient implementations. \textbf{Stack:} Ethical Hacking, Docker, Git.}
\end{cvskills}
\end{cvsection}

% --- EXPERIENCE ---
\begin{cvsection}{Professional Experience}
\begin{cventries}

  \cventry
    {Technical Project Lead (Contract)}
    {Steadfast Security Inc.}
    {Remote}
    {Project-based}
    {
      \begin{cvitems}
        \item {Delivered the digital identity rollout and a high-performance website with secure architecture.}
        \item {Hardened forms and encrypted data handling to protect sensitive leads.}
        \item {Documented and deployed with traceable change control.}
      \end{cvitems}
    }

  \cventry
    {E-commerce \& Growth Specialist}
    {Ceremonias Barcelona}
    {Barcelona, ES / Remote}
    {Project-based}
    {
      \begin{cvitems}
        \item {Re-engineered Shopify for CRO and performance across high-volume catalogs.}
        \item {Integrated Klaviyo and Recharge for lifecycle flows and subscriptions.}
        \item {Optimized Core Web Vitals and speed budgets for mobile-first growth.}
      \end{cvitems}
    }

  \cventry
    {Growth Engineer \& Founder}
    {Xpertasocial}
    {Mexico / Remote}
    {Jan 2018 -- Present}
    {
      \begin{cvitems}
        \item {Migrated sites to headless architectures (Vercel/Next.js) to improve speed and conversion.}
        \item {Designed landing systems with CRO testing and revenue measurement by cohort.}
        \item {Automated deployments with Docker for production reproducibility.}
      \end{cvitems}
    }

\end{cventries}
\end{cvsection}

% --- PROJECTS ---
\begin{cvsection}{Technical Projects \& Labs}
\begin{cvitems}
  \item {\textbf{Dockerized Commerce Environments:} reproducible Shopify/Next.js setups that remove "works on my machine" friction.}
  \item {\textbf{iOS Dev Environment (iSH/Vim/Git):} mobile hot-fixes for critical campaigns with version control.}
\end{cvitems}
\end{cvsection}

% --- STACK ---
\begin{cvsection}{Stack \& Tooling}
\begin{cvskills}
  \cvskill
    {Web \& CRO}
    {Next.js (App Router), Shopify (Liquid/Klaviyo/Recharge), Webflow, Tailwind CSS.}

  \cvskill
    {Infra \& DevOps}
    {Docker, Vercel, Git, CI/CD, Bash/Zsh.}

  \cvskill
    {Growth}
    {Meta Ads, GA4, A/B Testing, Technical SEO.}
\end{cvskills}
\end{cvsection}

% --- LINKS ---
\begin{cvsection}{Links}
\begin{cvitems}
  \item {\textbf{Site:} \href{https://www.xperta.social/}{xperta.social} \quad
        \textbf{GitHub:} \href{https://github.com/lbaddass}{github.com/lbaddass} \quad
        \textbf{LinkedIn:} \href{https://www.linkedin.com/in/jlgarciaorobio/}{jlgarciaorobio}}
  \item {\textbf{X:} \href{https://x.com/lbaddassl}{x.com/lbaddassl} \quad
        \textbf{Facebook:} \href{https://www.facebook.com/lbaddassl}{facebook.com/lbaddassl} \quad
        \textbf{Pinterest:} \href{https://mx.pinterest.com/lbaddassl/}{pinterest.com/lbaddassl}}
\end{cvitems}
\end{cvsection}

\makecvfooter{\today}{José Luis García Orobio}{\thepage}
\end{document}
