% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
\documentclass[11pt, a4paper]{../../awesome-cv/awesome-cv}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% --- PERSONAL DATA ---
\name{José Luis}{García Orobio}
\position{Automation Architect{\enskip\cdotp\enskip}Marketing Ops}
\address{Mexico (Remote/Hybrid){\enskip\textbar\enskip}Immediate availability}

\email{tu-email@dominio.com}
\homepage{www.xperta.social}
\github{lbaddass}
\linkedin{jlgarciaorobio}
\twitter{lbaddassl}

\quote{``I connect silos and turn static databases into automated revenue flows.''}

\begin{document}

% Header
\makecvheader[C]

% --- PROFILE SUMMARY ---
\begin{cvsection}{Profile Summary}
\begin{cvparagraph}
Automation architect focused on \textbf{Marketing Ops}. I design middleware and workflows that connect CRM, paid media, and fulfillment to remove operational friction. I combine \textbf{Python scripting}, \textbf{Make/Zapier} integrations, and \textbf{local-first} tooling (Raycast/MCP) to orchestrate reliable, measurable systems.
\end{cvparagraph}
\end{cvsection}

% --- PERFORMANCE & SECURITY AUDIT ---
\begin{cvsection}{Performance \& Security Audit}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} p{0.32\textwidth} p{0.62\textwidth}}
\textbf{You Get (Employer)} & \textbf{I Provide (The Stack)} \\
\hline
\textbf{Hybrid Agility} & I connect business needs with automation without bottlenecks. \\
\textbf{Black Box Tech} & Proprietary script library (Raycast/Python) to orchestrate processes 10x faster. \\
\textbf{Deep Work Ethic} & Operational documentation, metrics, and traceability in every flow. \\
\end{tabular*}
\end{cvsection}

% --- HYBRID IDENTITY STACK ---
\begin{cvsection}{Hybrid Identity Stack}
\begin{cvskills}
  \cvskill
    {Automation Ops}
    {Connected CRM and data flows. \textbf{Stack:} Make/Zapier, HubSpot, Salesforce, Webhooks.}

  \cvskill
    {Scripting \& Middleware}
    {Local-first automation. \textbf{Stack:} Python, Bash/Zsh, Raycast/MCP, APIs.}

  \cvskill
    {Revenue Systems}
    {Marketing ops with ROAS visibility. \textbf{Stack:} Meta Ads, GA4, Looker Studio.}
\end{cvskills}
\end{cvsection}

% --- EXPERIENCE ---
\begin{cvsection}{Professional Experience}
\begin{cventries}

  \cventry
    {Growth Engineer \& Founder}
    {Xpertasocial}
    {Mexico / Remote}
    {Jan 2018 -- Present}
    {
      \begin{cvitems}
        \item {Designed automations to synchronize CRM, campaigns, and catalogs using Python scripts.}
        \item {Built reporting flows and alerts for fast, performance-based decisions.}
        \item {Integrated Server-side GTM + CAPI to ensure conversion data integrity.}
      \end{cvitems}
    }

  \cventry
    {Marketing Ops Architect}
    {ONIBEX}
    {Remote}
    {Project-based}
    {
      \begin{cvitems}
        \item {Designed lead nurturing workflows connecting forms, CRM, and retargeting campaigns.}
        \item {Implemented automated lead validation and scoring to prioritize sales.}
      \end{cvitems}
    }

  \cventry
    {Lifecycle Automation Consultant}
    {Oowlish}
    {Remote}
    {Project-based}
    {
      \begin{cvitems}
        \item {Automated Klaviyo + Recharge flows for retention and revenue recovery.}
        \item {Behavior-based segmentation to lift LTV.}
      \end{cvitems}
    }

\end{cventries}
\end{cvsection}

% --- PROJECTS ---
\begin{cvsection}{Technical Projects \& Labs}
\begin{cvitems}
  \item {\textbf{Local-First Command Center:} Raycast + Python scripts to orchestrate tasks and assets in real time.}
  \item {\textbf{iOS Dev Environment (iSH/Vim/Git):} critical operations from mobile with synced repos.}
\end{cvitems}
\end{cvsection}

% --- STACK ---
\begin{cvsection}{Stack \& Tooling}
\begin{cvskills}
  \cvskill
    {Automation}
    {Python (Scripting), Make.com, Zapier, Webhooks, APIs.}

  \cvskill
    {CRM \& Lifecycle}
    {HubSpot, Salesforce, Klaviyo, Recharge, Lead Scoring.}

  \cvskill
    {Ops \& Analytics}
    {Raycast/MCP, GA4, Looker Studio, Git, Bash/Zsh.}
\end{cvskills}
\end{cvsection}

% --- LINKS ---
\begin{cvsection}{Links}
\begin{cvitems}
  \item {\textbf{Site:} \href{https://www.xperta.social/}{xperta.social} \quad
        \textbf{GitHub:} \href{https://github.com/lbaddass}{github.com/lbaddass} \quad
        \textbf{LinkedIn:} \href{https://www.linkedin.com/in/jlgarciaorobio/}{jlgarciaorobio}}
  \item {\textbf{X:} \href{https://x.com/lbaddassl}{x.com/lbaddassl} \quad
        \textbf{Facebook:} \href{https://www.facebook.com/lbaddassl}{facebook.com/lbaddassl} \quad
        \textbf{Pinterest:} \href{https://mx.pinterest.com/lbaddassl/}{pinterest.com/lbaddassl}}
\end{cvitems}
\end{cvsection}

\makecvfooter{\today}{José Luis García Orobio}{\thepage}
\end{document}
