% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
\documentclass[11pt, a4paper]{../../awesome-cv/awesome-cv}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% --- PERSONAL DATA ---
\name{José Luis}{García Orobio}
\position{Technical SEO{\enskip\cdotp\enskip}Programmatic SEO}
\address{Mexico (Remote/Hybrid){\enskip\textbar\enskip}Immediate availability}

\email{tu-email@dominio.com}
\homepage{www.xperta.social}
\github{lbaddass}
\linkedin{jlgarciaorobio}
\twitter{lbaddassl}

\quote{``I don't just write content; I structure data so machines can understand it.''}

\begin{document}

% Header
\makecvheader[C]

% --- PROFILE SUMMARY ---
\begin{cvsection}{Profile Summary}
\begin{cvparagraph}
Technical SEO and \textbf{Programmatic SEO} specialist. I design data pipelines that turn catalogs and databases into thousands of landing pages with validated \textbf{Schema.org}. I combine log analysis, scraping, and SQL to map entities and scale organic traffic with precision.
\end{cvparagraph}
\end{cvsection}

% --- PERFORMANCE & SECURITY AUDIT ---
\begin{cvsection}{Performance \& Security Audit}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} p{0.32\textwidth} p{0.62\textwidth}}
\textbf{You Get (Employer)} & \textbf{I Provide (The Stack)} \\
\hline
\textbf{Hybrid Agility} & I connect content, data, and architecture for sustainable organic growth. \\
\textbf{Business Logic} & Revenue-first SEO: keywords prioritized by intent and margin. \\
\textbf{Deep Work Ethic} & Audits documented with traceability and remediation plans. \\
\end{tabular*}
\end{cvsection}

% --- HYBRID IDENTITY STACK ---
\begin{cvsection}{Hybrid Identity Stack}
\begin{cvskills}
  \cvskill
    {Technical SEO}
    {Programmatic SEO and data structuring. \textbf{Stack:} Python, JSON-LD, Screaming Frog, SQL.}

  \cvskill
    {Data Engineering}
    {Normalization, clustering, and metadata QA. \textbf{Stack:} Pandas, Regex, Log Analysis.}

  \cvskill
    {Content Systems}
    {Taxonomies and internal linking at scale. \textbf{Stack:} Schema.org, Crawling, CMS.}
\end{cvskills}
\end{cvsection}

% --- EXPERIENCE ---
\begin{cvsection}{Professional Experience}
\begin{cventries}

  \cventry
    {Senior Digital Architect}
    {Martom Sport}
    {LatAm / Remote}
    {Previous tenure}
    {
      \begin{cvitems}
        \item {Scaled massive catalogs with Programmatic SEO: automated Schema.org injection and Python landing generation.}
        \item {Optimized feeds and taxonomies to capture long-tail transactional intent.}
        \item {Audited logs and improved Core Web Vitals to sustain high-volume indexing.}
      \end{cvitems}
    }

  \cventry
    {Growth Engineer / SEO Automation}
    {Xpertasocial}
    {Mexico / Remote}
    {2021 -- Present}
    {
      \begin{cvitems}
        \item {Python/Bash scripts for ethical scraping, dataset normalization, and large-scale metadata QA.}
        \item {Information architecture based on semantic clusters and internal linking to optimize crawl budget.}
        \item {Programmatic SEO with dynamic templates and JSON-LD structured data.}
      \end{cvitems}
    }

  \cventry
    {Technical SEO Consultant}
    {Law Offices of Vlad Portnoy}
    {Remote}
    {Project-based}
    {
      \begin{cvitems}
        \item {Designed an AI-driven SEO strategy to scale pages by entities and legal services.}
        \item {Implemented advanced schema to improve CTR and eligibility for rich results.}
      \end{cvitems}
    }

\end{cventries}
\end{cvsection}

% --- PROJECTS ---
\begin{cvsection}{Technical Projects \& Labs}
\begin{cvitems}
  \item {\textbf{Programmatic Landing Factory:} Python pipeline to generate, validate, and publish landing pages at scale.}
  \item {\textbf{Search Console Log Intelligence:} log analysis to detect cannibalization and zombie pages.}
\end{cvitems}
\end{cvsection}

% --- STACK ---
\begin{cvsection}{Stack \& Tooling}
\begin{cvskills}
  \cvskill
    {SEO \& Data}
    {Python (Pandas/BeautifulSoup), SQL, Screaming Frog, Schema.org (JSON-LD), Regex.}

  \cvskill
    {Crawling \& QA}
    {Log Analysis, Sitebulb, Ahrefs, Semrush, GSC/GA4.}

  \cvskill
    {CMS \& Dev}
    {WordPress, Shopify, HTML/CSS, Git, Bash/Zsh.}
\end{cvskills}
\end{cvsection}

% --- LINKS ---
\begin{cvsection}{Links}
\begin{cvitems}
  \item {\textbf{Site:} \href{https://www.xperta.social/}{xperta.social} \quad
        \textbf{GitHub:} \href{https://github.com/lbaddass}{github.com/lbaddass} \quad
        \textbf{LinkedIn:} \href{https://www.linkedin.com/in/jlgarciaorobio/}{jlgarciaorobio}}
  \item {\textbf{X:} \href{https://x.com/lbaddassl}{x.com/lbaddassl} \quad
        \textbf{Facebook:} \href{https://www.facebook.com/lbaddassl}{facebook.com/lbaddassl} \quad
        \textbf{Pinterest:} \href{https://mx.pinterest.com/lbaddassl/}{pinterest.com/lbaddassl}}
\end{cvitems}
\end{cvsection}

\makecvfooter{\today}{José Luis García Orobio}{\thepage}
\end{document}
