% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
\documentclass[11pt, a4paper]{../../awesome-cv/awesome-cv}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% --- PERSONAL DATA ---
\name{José Luis}{García Orobio}
\position{Full-Stack Growth Engineer{\enskip\cdotp\enskip}Marketing Architect}
\address{Mexico (Remote/Hybrid){\enskip\textbar\enskip}Immediate availability}

\email{tu-email@dominio.com}
\homepage{www.xperta.social}
\github{lbaddass}
\linkedin{jlgarciaorobio}
\twitter{lbaddassl}

\quote{``I don't just run campaigns or code; I orchestrate automated revenue systems.''}

\begin{document}

% Header
\makecvheader[C]

% --- PROFILE SUMMARY ---
\begin{cvsection}{Profile Summary}
\begin{cvparagraph}
Technical leader with 12+ years bridging \textbf{performance marketing} and \textbf{software engineering}. I build sales machines where ad infrastructure, headless architectures, and CRM automation operate as one revenue circuit. My background as a \textbf{Senior Ethical Hacker} ensures reliable deployments, data integrity, and decisions validated by metrics.
\end{cvparagraph}
\end{cvsection}

% --- PERFORMANCE & SECURITY AUDIT ---
\begin{cvsection}{Performance \& Security Audit}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} p{0.32\textwidth} p{0.62\textwidth}}
\textbf{You Get (Employer)} & \textbf{I Provide (The Stack)} \\
\hline
\textbf{Hybrid Agility} & I speak "Client" (Marketing) and "Server" (Dev). No translation friction. \\
\textbf{Deep Work Ethic} & Validated by the "Steadfast" mode: I document, record, and deliver with traceability. \\
\textbf{Black Box Tech} & Access to my proprietary automation library (Raycast/Python) to execute 10x faster. \\
\textbf{Business Logic} & I don't code for aesthetics; I code for conversion (ROAS/ROI/SEO). \\
\end{tabular*}
\end{cvsection}

% --- HYBRID IDENTITY STACK ---
\begin{cvsection}{Hybrid Identity Stack}
\begin{cvskills}
  \cvskill
    {Growth Engineer}
    {I build CRO-driven sales machines. \textbf{Stack:} Next.js, Shopify Liquid, Webflow, PHP.}

  \cvskill
    {AdTech Specialist}
    {Tracking audits (CAPI/Server-side) to guarantee ROAS. \textbf{Stack:} Meta Ads, GTM, Graph API.}

  \cvskill
    {Technical SEO}
    {Programmatic SEO and data structuring at scale. \textbf{Stack:} Python, JSON-LD, Bash, Screaming Frog.}

  \cvskill
    {Automation Ops}
    {CRM and data flows connected via custom middleware. \textbf{Stack:} HubSpot/Salesforce, Make/Zapier, Raycast, APIs.}
\end{cvskills}
\end{cvsection}

% --- EXPERIENCE ---
\begin{cvsection}{Professional Experience}
\begin{cventries}

  \cventry
    {Growth Engineer \& Founder}
    {Xpertasocial}
    {Mexico / Remote}
    {Jan 2018 -- Present}
    {
      \begin{cvitems}
        \item {Designed full-funnel \textit{growth frameworks} integrating Next.js frontends with Meta Ads automation loops to sustain 3x-5x ROAS.}
        \item {Implemented Server-side GTM + CAPI and data integrity audits to close attribution gaps and protect multi-brand budgets.}
        \item {Migrated sites to headless architectures (Vercel/Next.js), improving CWV and lifting organic conversions by 25\% on average.}
      \end{cvitems}
    }

  \cventry
    {Technical Project Lead (Contract)}
    {Steadfast Security Inc.}
    {Remote}
    {Project-based}
    {
      \begin{cvitems}
        \item {Led the digital identity rollout (branding, uniform systems, high-performance site) with a security-first approach.}
        \item {Applied ethical hacking principles to harden forms and encrypt sensitive lead handling.}
        \item {Automated documentation workflows with Raycast/MCP to maintain a single source of truth.}
      \end{cvitems}
    }

  \cventry
    {E-commerce \& Growth Specialist}
    {Ceremonias Barcelona}
    {Barcelona, ES / Remote}
    {Project-based}
    {
      \begin{cvitems}
        \item {Re-engineered Shopify for CRO, integrating Klaviyo (lifecycle) and Recharge (subscriptions).}
        \item {Deployed Meta Ads campaigns with broad targeting and high-volume creative testing.}
        \item {Programmatic feed and inventory management for Meta Shops and Google Merchant Center.}
      \end{cvitems}
    }

\end{cventries}
\end{cvsection}

% --- PROJECTS ---
\begin{cvsection}{Technical Projects \& Labs}
\begin{cvitems}
  \item {\textbf{Project "Nano Banana" (Gemini AI):} pipeline for product image editing using Gemini vision models.}
  \item {\textbf{iOS Dev Environment (iSH/Vim/Git):} local-first setup for hot-fixes in Next.js/Python with mobile Git control.}
  \item {\textbf{Meta Ads Creative Strategist (TAS Digital):} "Creative-Led Growth" framework driven by data-based hooks.}
\end{cvitems}
\end{cvsection}

% --- STACK ---
\begin{cvsection}{Stack \& Tooling}
\begin{cvskills}
  \cvskill
    {Development}
    {Next.js, Shopify (Liquid/Klaviyo/Recharge), Webflow, PHP, Python (Pandas/Scraping), Docker, Git.}

  \cvskill
    {Marketing Tech}
    {Meta Business Suite (Advanced Broad/CAPI), Google Ads, Technical SEO, CRM Automation, Looker Studio.}

  \cvskill
    {Ops \& Security}
    {Ethical Hacking (12+ years), Server-side GTM, Vercel, Raycast Automation, Bash/Zsh, APIs.}
\end{cvskills}
\end{cvsection}

% --- LINKS ---
\begin{cvsection}{Links}
\begin{cvitems}
  \item {\textbf{Site:} \href{https://www.xperta.social/}{xperta.social} \quad
        \textbf{GitHub:} \href{https://github.com/lbaddass}{github.com/lbaddass} \quad
        \textbf{LinkedIn:} \href{https://www.linkedin.com/in/jlgarciaorobio/}{jlgarciaorobio}}
  \item {\textbf{X:} \href{https://x.com/lbaddassl}{x.com/lbaddassl} \quad
        \textbf{Facebook:} \href{https://www.facebook.com/lbaddassl}{facebook.com/lbaddassl} \quad
        \textbf{Pinterest:} \href{https://mx.pinterest.com/lbaddassl/}{pinterest.com/lbaddassl}}
\end{cvitems}
\end{cvsection}

\makecvfooter{\today}{José Luis García Orobio}{\thepage}
\end{document}
