% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
\documentclass[11pt, a4paper]{../../awesome-cv/awesome-cv}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% --- PERSONAL DATA ---
\name{José Luis}{García Orobio}
\position{AdTech Specialist{\enskip\cdotp\enskip}Paid Media \& Tracking}
\address{Mexico (Remote/Hybrid){\enskip\textbar\enskip}Immediate availability}

\email{tu-email@dominio.com}
\homepage{www.xperta.social}
\github{lbaddass}
\linkedin{jlgarciaorobio}
\twitter{lbaddassl}

\quote{``I don't just buy traffic; I audit the infrastructure to guarantee ROAS.''}

\begin{document}

% Header
\makecvheader[C]

% --- PROFILE SUMMARY ---
\begin{cvsection}{Profile Summary}
\begin{cvparagraph}
Paid Media and \textbf{Attribution Engineering} specialist. I resolve the attribution crisis by auditing tracking at the server layer with \textbf{CAPI} and \textbf{GTM Server-side} so every dollar in Meta/Google is accurately measured. I design creative feedback loops based on data (hook-rate and hold-rate), optimizing ROAS through fast iterations, not guesses.
\end{cvparagraph}
\end{cvsection}

% --- PERFORMANCE & SECURITY AUDIT ---
\begin{cvsection}{Performance \& Security Audit}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} p{0.32\textwidth} p{0.62\textwidth}}
\textbf{You Get (Employer)} & \textbf{I Provide (The Stack)} \\
\hline
\textbf{Hybrid Agility} & I translate Marketing needs into Server/Tracking logic without friction. \\
\textbf{Black Box Tech} & Proprietary automation library (Raycast/Python) to accelerate creative optimization and reporting. \\
\end{tabular*}
\end{cvsection}

% --- HYBRID IDENTITY STACK ---
\begin{cvsection}{Hybrid Identity Stack}
\begin{cvskills}
  \cvskill
    {AdTech Specialist}
    {Robust tracking infrastructure. \textbf{Stack:} Meta Ads (Andromeda), GTM Server-side, CAPI, Graph API.}

  \cvskill
    {Creative Data Engineering}
    {Hook analysis and testing pipelines. \textbf{Stack:} Python, FFmpeg, Looker Studio.}

  \cvskill
    {Growth Engineer}
    {Conversion-optimized landings and funnels. \textbf{Stack:} Next.js, Webflow, Shopify Liquid.}
\end{cvskills}
\end{cvsection}

% --- EXPERIENCE ---
\begin{cvsection}{Professional Experience}
\begin{cventries}

  \cventry
    {Growth Engineer \& Founder}
    {Xpertasocial}
    {Mexico / Remote}
    {Jan 2018 -- Present}
    {
      \begin{cvitems}
        \item {Architected Meta Ads campaigns (Andromeda logic) with tracking audits to sustain 3x-5x ROAS.}
        \item {Implemented Server-side GTM + CAPI to recover attribution post-iOS14 and improve match rates.}
        \item {Automated creative production with Python + FFmpeg to speed test cycles and cut time-to-market by 70\%.}
      \end{cvitems}
    }

  \cventry
    {Paid Media \& Tracking Specialist}
    {Ceremonias Barcelona}
    {Barcelona, ES / Remote}
    {Project-based}
    {
      \begin{cvitems}
        \item {Deployed Meta Ads campaigns for high-intent niches using broad targeting and data-driven creative.}
        \item {Optimized purchase events and quality signals to improve Shopify attribution.}
        \item {Integrated catalogs and feeds for Meta Shops and Google Merchant Center.}
      \end{cvitems}
    }

  \cventry
    {AdTech Strategy Consultant}
    {TAS Digital Agency Framework}
    {Remote}
    {Project-based}
    {
      \begin{cvitems}
        \item {Implemented the "Creative-Led Growth" framework with broad targeting and data-backed creative testing.}
        \item {Built performance dashboards to detect hook decay and adjust creatives weekly.}
      \end{cvitems}
    }

\end{cventries}
\end{cvsection}

% --- PROJECTS ---
\begin{cvsection}{Technical Projects \& Labs}
\begin{cvitems}
  \item {\textbf{Attribution Recovery Playbook:} audit checklist for CAPI/GTM Server-side when signal loss hits.}
  \item {\textbf{Hook-Rate Analyzer:} Python scripts to score video ad retention and prioritize iterations.}
\end{cvitems}
\end{cvsection}

% --- STACK ---
\begin{cvsection}{Stack \& Tooling}
\begin{cvskills}
  \cvskill
    {AdTech}
    {Meta Business Suite (Advanced Broad/CAPI), Google Ads, GTM Server-side, Facebook Graph API.}

  \cvskill
    {Data \& Creative Ops}
    {Python (Pandas/Scripting), FFmpeg, Looker Studio, GA4, UTM Governance.}

  \cvskill
    {Dev \& CRO}
    {Next.js, Shopify (Liquid), Webflow, Vercel, Git.}
\end{cvskills}
\end{cvsection}

% --- LINKS ---
\begin{cvsection}{Links}
\begin{cvitems}
  \item {\textbf{Site:} \href{https://www.xperta.social/}{xperta.social} \quad
        \textbf{GitHub:} \href{https://github.com/lbaddass}{github.com/lbaddass} \quad
        \textbf{LinkedIn:} \href{https://www.linkedin.com/in/jlgarciaorobio/}{jlgarciaorobio}}
  \item {\textbf{X:} \href{https://x.com/lbaddassl}{x.com/lbaddassl} \quad
        \textbf{Facebook:} \href{https://www.facebook.com/lbaddassl}{facebook.com/lbaddassl} \quad
        \textbf{Pinterest:} \href{https://mx.pinterest.com/lbaddassl/}{pinterest.com/lbaddassl}}
\end{cvitems}
\end{cvsection}

\makecvfooter{\today}{José Luis García Orobio}{\thepage}
\end{document}
